Introduction

### 2015-07-22 dissertation/related.tex
reformulate sigmod relation

Montoya et al. \cite{DBLP:journals/corr/MontoyaSMV15} proposes a query
federation system that takes advantage of client-side data
replication.

>>>>

Recently, Papailiou et al. \cite{papailiou2015graph} made an extensive
study of SPARQL caching, addressing some of the same problems as the
present work, except for our emphasis on deployment on proxies in the
Internet and integration with HTTP-based caching.  Montoya et
al. \cite{DBLP:journals/corr/MontoyaSMV15} proposes a query federation
system that takes advantage of client-side data replication. Both
these studies claim to support the entire SPARQL query language, but
in both cases, it is not clear that they actually do that.
